Stat_490_Paper

### 2020-05-05 Paper.Rmd
Paper Update
- Added Summary Statistics for cms using span:
15, 25, 35, 45, 55, 65, 75, and 85
- Added ROC plots for cms using span:
15, 25, 35, 45, 55, 65, 75, 85
- Added AUC outputs for different spans
- Added Images(Still need some more and maybe need to remove some)
- Images are currently inserted using code chunk with the image path being on my personal computer
- Models are currently running for comparisons

---
title: "Stat_490"
author: "Andrew Maloney"
date: "4/28/2020"
output: html_document
---

@@

@@

@@

@@

@@

@@

@@

... to be continued

@@

```{r}

@@

@@

>>>>

---
title: "Stat_490_Paper"
author: "Andrew Maloney"
date: "5/5/2020"
output: html_document
---

@@

![Scan 1 Sampled](/Users/piza7/Pictures/Paper_1_samp.png)

![Scan 11 Sampled](/Users/piza7/Pictures/Paper_11_samp.png)

![Scan 111 Sampled](/Users/piza7/Pictures/Paper_111_samp.png)

@@

![Scan 1](/Users/piza7/Pictures/Paper_1_nosamp.png)

![Scan 11](/Users/piza7/Pictures/Paper_11_nosamp.png)

![Scan 111](/Users/piza7/Pictures/Paper_111_nosamp.png)

@@

![Before Cutoff](/Users/piza7/Pictures/Paper_Groove_before_Cut.png)

![Cutoff](/Users/piza7/Pictures/Paper_Groove_Cut.png)

@@

```{r, echo=FALSE}
knitr::include_graphics("/Users/piza7/Pictures/ResidualPlot.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("/Users/piza7/Pictures/smoothing.png")
```

@@

```{r, echo=FALSE}
knitr::include_graphics("/Users/piza7/Pictures/AlignedSignatures.png")
```

@@

## Summary Statistics

[1] implies same comparisons are kept for statistical summary

[2] implies same comparisons are removed for statistical summary

*Span of 15:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   2.000   3.000   3.141   4.000  73.000 [1]

0.000   2.000   3.000   2.872   4.000  34.000 [2]

_____________________________________________________________________________________________

*Span of 25:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   2.000   3.000   3.062   3.000  62.000 [1]

0.000   2.000   2.000   2.827   3.000  37.000 [2]

_____________________________________________________________________________________________

*Span of 35:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   2.000   2.000   2.974   3.000  56.000 [1]

0.000   2.000   2.000   2.776   3.000  32.000 [2]

_____________________________________________________________________________________________

*Span of 45:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   2.000   2.000   2.915   3.000  47.000 [1]

0.000   2.000   2.000   2.745   3.000  37.000 [2]

_____________________________________________________________________________________________

*Span of 55:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   1.000   2.000   2.832   3.000  41.000 [1]

0.000   1.000   2.000   2.685   3.000  34.000 [2]

_____________________________________________________________________________________________

*Span of 65:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   1.000   2.000   2.698   3.000  37.000 [1]

0.000   1.000   2.000   2.569   3.000  34.000 [2]

_____________________________________________________________________________________________

*Span of 75:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   1.000   2.000   2.557   3.000  34.000 [1]

0.000   1.000   2.000   2.442   3.000  25.000 [2]

_____________________________________________________________________________________________

*Span of 85:*

Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

0.000   1.000   2.000   2.451   3.000  30.000 [1]

0.000   1.000   2.000   2.349   3.000  23.000 [2]

_____________________________________________________________________________________________

## AUC Calculations No Samp

![Distinct](/Users/piza7/Pictures/Paper_ROC_Distinct.png)

![Non Distinct](/Users/piza7/Pictures/Paper_ROC_NonDistinct.png)

Span of 15: Area under the curve: 0.6414

Span of 25: Area under the curve: 0.6498

Span of 35: Area under the curve: 0.6487

Span of 45: Area under the curve: 0.6577

Span of 55: Area under the curve: 0.6611

Span of 65: Area under the curve: 0.6614

Span of 75: Area under the curve: 0.6606

Span of 85: Area under the curve: 0.6602

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_15 <- Phoenix_Comparisons_25 %>%
  mutate(Bullet1 = gsub(" ", "", fixed = TRUE, Bullet1), Bullet2 = gsub(" ", "", fixed = TRUE, Bullet2))

Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(BarrelA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\1", Bullet2))
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(BarrelB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\1", Bullet1))
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(BulletA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\2", Bullet2))
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(BulletB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\2", Bullet1))
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(LandA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\3", Bullet2))
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
  mutate(LandB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\3", Bullet1))

Phoenix_Comparisons_85 <- Phoenix_Comparisons_85 %>% mutate(
  comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2))
)

```{r eval=FALSE, include=FALSE}
Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_15 <- distinct(Phoenix_Comparisons_15, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_15$cms)

```{r eval=FALSE, include=FALSE}
Phoenix_Comparisons_25 <- Phoenix_Comparisons_25 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_25 <- distinct(Phoenix_Comparisons_25, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_25$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_35 <- Phoenix_Comparisons_35 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_35 <- distinct(Phoenix_Comparisons_35, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_35$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_45 <- Phoenix_Comparisons_45 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_45 <- distinct(Phoenix_Comparisons_45, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_45$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_55 <- Phoenix_Comparisons_55 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_55 <- distinct(Phoenix_Comparisons_55, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_55$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_65 <- Phoenix_Comparisons_65 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_65 <- distinct(Phoenix_Comparisons_65, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_65$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_75 <- Phoenix_Comparisons_75 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_75 <- distinct(Phoenix_Comparisons_75, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_75$cms)

```{r eval=FALSE, include=FALSE}

Phoenix_Comparisons_85 <- Phoenix_Comparisons_85 %>% filter(Bullet1 != Bullet2)

Phoenix_Comparisons_85 <- distinct(Phoenix_Comparisons_85, comparison, .keep_all= TRUE)

summary(Phoenix_Comparisons_85$cms)

@@

```{r eval=FALSE, include=FALSE}

@@

```{r eval=FALSE, include=FALSE}

@@

Phoenix <- Phoenix %>% mutate(x3p = map(x3p, sample_x3p, m = 2, mY = 2))

image(Phoenix$x3p[[1]])
image(Phoenix$x3p[[11]])
image(Phoenix$x3p[[111]])
